---
title: "General use of the package"
author: "Roel M. Hogervorst"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{General use of the package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Badgecreatr was developed with myself in mind. I often create packages on github
and wanted to have a standardized way to add badges to the readme. In github the
readme file on top of the repository is automatically rendered as html and can
be viewed by everyone. 

I've written a blogpost about the package [here](http://rmhogervorst.nl/cleancode/blog/2016/07/08/introducing-badgecreatr-create-and-place-badges-in-readme-rmd.html)

## Badges or shields
Many projects have shields that signal the status of the project. When you make
use of continuous integration tools such as [travis-ci](https://docs.travis-ci.com/user/languages/r "a R-specific guide for travis"), you let the service rebuild and retest your package after every
commit to github. Travis has a badge that signals if the build passed or not. 
I've added extra information such as under what licence the code is shared, 
the latest change in the package and what version the package has. 

Keep in mind that I don't create all of the badges (only 2 are of my invention), 
this package is just a convenient way to place badges in your readme. 

# Use cases
I realized that I don't often use the package in it's original form anymore, 
so the use cases might change. I've identified some cases.

- [] scenario 0: you just want to add a few loose badges
- [] scenario 1: starting a package with minimal badges.
- [] scenario 2: base version but with logic added to seperate code part that tracks changes to R version, change date and versions.
- [] scenario 3: you already have some badges, but you want to add newer ones (cran, rdocumentation, travis, etc).
- [] scenario 4: you want to add certain badges, essentially a list of badges that you want, regardless of whats already there (so it should ignore badges, ignore if there is a travis file)

### Scenario 0: add a few loose badges
You just want to add a badge for projectstatus.
```{r scen 0}
library(badgecreatr)
projectstatusbadge("wip") # any of concept, wip, suspended, abandoned, active, inactive, unsupported
```

This results in markdown that you can paste into your readme file.
Other badges could be `last_change_badge_static` This would input the current 
date. 

### Scenario 1: starting a package with minimal badges
I imagin using this to add some quick badges that you might update later
but it communicates the basic properties of the package:

- Maturity (project status)
- Licence
- Last change

```{r scen 1}
minimal_badges("concept", "MIT")
```
